### 2015-07-20 src/intro/intro.tex
Fixed minor mistakes.
Updated to intro after review comments.

\subsubsection{Landmarks}
In addition to relative cues, the brain seems to use absolute cues in both the perception of gravity and self-motion. For the perception of gravity, it makes use of the fact that many lines within the world are aligned with either the horizon or gravity (\panelref{intro:fig:treeframe}{A}). Straight lines therefore acts as a priors attracting the perceived direction of gravity towards them. A special case is the rod-and-frame illusion (\panelref{intro:fig:treeframe}{B}), where the perceived angle of a rod relative to gravity is affected by the orientation of the frame that contains it \cite{witkin1948}.

@@

We will now briefly explain the mathematical foundations of optimal integration. Suppose there is a true physical stimulus in the world, $x$, which is observed by multiple sensory systems, $x_i$. We assume that these observations are corrupted by independent Gaussian noise, $\sigma_i^2$. The probability of the observations, $x_i$, given the stimulus $x$, is therefore:

@@

From the point of view of the brain, the observations, $x_i$, are given while the stimulus, $x$, has to be inferred. In this case, probability $P(x_i|x)$ is referred to as the likelihood of the stimulus given the observations, or $\mathcal{L}(x|x_i)$. Given multiple sensory observations, $x_1,\dotsc,x_n$, we can now compute the likelihood of the stimulus:

\begin{equation}
\mathcal{L}(x|x_1,\dotsc,x_n) = P(x_1,\dotsc,x_n|x) = \prod_i P(x_i|x)
\end{equation}

@@

\begin{equation}
\hat{x}=\sum_i w_i x_i
\end{equation}

@@

\begin{equation}
w_i = \frac{1/\sigma^2_i}{\sum_j 1/\sigma^2_j}
\end{equation}

@@

\begin{equation}
\hat{\sigma}^2_i = \frac{\prod_i \sigma^2_i}{\sum_i \sigma^2_i}
\end{equation}

@@

A powerful tool in psychophysical research is the two-alternative forced choice (2AFC) paradigm. In this paradigm, participants are presented with two stimuli, e.g. two translation distances, and are then forced to make a choice, e.g. on which of the two translations was longer. By systematically varying one of the choice alternatives (i.e., the probe stimulus), the point of subjective equality, or PSE, can be determined. The PSE is the point at which the participant is completely unsure about which stimulus to pick, i.e. gives a random response, because the participant perceives the two stimuli as being equal. If the PSE does not line up with the actual reference stimulus, there is a bias in the percept, represented by the Greek letter mu ($\mu$).

In addition to establishing perceptual equality, the 2AFC paradigm also allows for quantifying the uncertainty in perception by looking at the slope of the psychometric curve around the PSE. This uncertainty is commonly quantified by the standard deviation of the cumulative Gaussian probability distribution that underlies the responses of the subject, represented by the Greek letter sigma ($\sigma$).

>>>>

\subsubsection{Landmarks}
In addition to relative cues, the brain seems to use absolute cues in both the perception of gravity and self-motion. For the perception of gravity, it makes use of the fact that many lines within the world are aligned with either the horizon or gravity (\panelref{intro:fig:treeframe}{A}). Straight lines therefore acts as priors attracting the perceived direction of gravity towards them. A special case is the rod-and-frame illusion (\panelref{intro:fig:treeframe}{B}), where the perceived angle of a rod relative to gravity is affected by the orientation of the frame that contains it \cite{witkin1948}.

@@

We will now briefly explain the mathematical foundations of optimal integration. Suppose there is a true physical stimulus in the world, $x$, which is observed by multiple sensory systems, $x_i$. We assume that these observations are corrupted by independent Gaussian noise, $\mathcal{N}(0, \sigma_i^2)$. The probability, $P$, of the observations, $x_i$, given the stimulus $x$, is therefore:

@@

From the point of view of the brain, the observations, $x_i$, are given while the stimulus, $x$, has to be inferred. In this case, probability $P(x_i|x)$ is referred to as the likelihood of the stimulus given the observations, or $\mathcal{L}(x|x_i)$. Given $n$ sensory observations, $x_1,\dotsc,x_n$, we can now compute the likelihood of the stimulus:

\begin{equation}
\mathcal{L}(x|x_1,\dotsc,x_n) = P(x_1,\dotsc,x_n|x) = \prod_{i=1}^n P(x_i|x)
\end{equation}

@@

\begin{equation}
\hat{x}=\sum_{i=1}^n w_i x_i
\end{equation}

@@

\begin{equation}
w_i = \frac{1/\sigma^2_i}{\sum_{j=1}^n 1/\sigma^2_j}
\end{equation}

@@

\begin{equation}
\hat{\sigma}^2_i = \frac{\prod_{i=1}^n \sigma^2_i}{\sum_{i=1}^n \sigma^2_i}
\end{equation}

@@

A powerful tool in psychophysical research is the two-alternative forced choice (2AFC) paradigm. In this paradigm, two alternatives are presented (e.g. lateral translations), after which participants are forced to make a choice between them (e.g. which was longer in distance). The probability of each response given the stimuli is mapped by systematically varying one stimulus, the probe, while keeping the other, the reference, constant.

The probability function underlying participant responses is called the psychometric function. In this thesis we use a commonly used psychometric function called the cumulative Gaussian function. The probability of a response given the probe stimulus, $x$, is then given by:

\begin{equation}
P(x) = \lambda + (1 - 2\lambda) \frac{1}{\sigma \sqrt{2\pi}} \int_{-\infty}^{x}{e^{-(y-PSE)^2 / 2\sigma^2}}dy,
\end{equation}

The mean of the Gaussian, $PSE$, represents the point of subjective equality, that is where the probe stimulus is perceived to be identical to the reference stimulus and the participant is thus unsure ($p = 0.5$) about which alternative to choose. When the PSE is equal to the reference stimulus performance is veridical, otherwise a bias, $\mu$, exists. The bias is quantified as the difference between the PSE and reference stimulus. The slope of the curve reflects the precision ($1/\sigma$) of reference-probe discrimination performance, and parameter $\lambda$ represents the lapse rate which accounts for stimulus-independent errors caused by subject lapses.
